\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Add transition between paragraphs.
Update fs-verity section.

%% Add transition to next section

@@

\subsection{fs-verity}
Fs-verity works similar to dm-verity, but instead of a hash tree for the whole
block device, fs-verity has a Merkle-Tree for every file in the File System
hidden after the last block of the file, but hidden from the normal
File System operations and the user.

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\end{thebibliography}
\end{document}

>>>>

In order to protect the File System's internal data structures as well as the
data stored in the File System both the internal structure and the payload
have to secured. A File System which has the possibility to do this, is BTRFS.

@@

\subsection{fs-verity}
Fs-verity\cite{FS-VERITY} works similar to dm-verity, but instead of a hash
tree for the whole block device, fs-verity has a Merkle-Tree for every file in
the File System hidden after the last block of the file, but hidden from the
normal File System operations and the user. The two differences to IMA are,
fs-verity a) uses a Merkle-Tree instead of a single hash, to speed up open(2)
calls and b) uses free space at the end of a file instead of an extended
attribute as this Merkle-Tree can grow larger than the maximum size of an
extended attribute. Fs-verity does not protect the File System's internal data
structures from being altered.

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\bibitem{FS-VERITY}
	J. Corbet
	\textit{Protecting files with fs-verity}
	\\\texttt{\href{https://lwn.net/Articles/763729/}{https://lwn.net/Articles/763729/}}
\end{thebibliography}
\end{document}
